[Artifact Presentation] Damegender: \\ Writing and Comparing Gender Detection Tools

### 2020-05-15 paper2sattose.tex
paper2sattose.tex: add Canada in ML table

\begin{table*}
\footnotesize
\begin{tabular}[]{lrrrrrrr}
  \hline
Dataset & a & last a & last o & last consonant & last vocal & 1st consonant & 1st vocal  \tabularnewline
  \hline
  %\endhead
 Uruguay (F) \footnote{F is for females and M is for males} &    0.816 &         0.456 &         0.007 &                 0.287 &             0.712 &                  0.823 &              0.177  \tabularnewline
 Uruguay (M) \footnotemark[3] &    0.643 &         0.249 &         0.062 &                 0.766 &             0.234 &                  0.771 &              0.228  \tabularnewline
 Spain (F) \footnotemark[3]  &    0.922 &         0.588 &          0.03 &                 0.271 &             0.728 &                  0.772 &              0.228  \tabularnewline
 Spain (M) \footnotemark[3]  &    0.818 &          0.03 &         0.268 &                 0.569 &              0.43 &                  0.763 &              0.236  \tabularnewline
 UK (F) \footnotemark[3]     &    0.825 &         0.374 &         0.013 &                 0.322 &             0.674 &                  0.765 &              0.235  \tabularnewline
 UK (M) \footnotemark[3]     &    0.716 &         0.036 &         0.039 &                  0.78 &             0.218 &                  0.799 &                0.2  \tabularnewline
 USA (F) \footnotemark[3]    &    0.816 &         0.456 &         0.007 &                 0.287 &             0.712 &                  0.823 &              0.177  \tabularnewline
 USA (M) \footnotemark[3]    &    0.643 &          0.02 &         0.061 &                 0.765 &             0.234 &                   0.84 &              0.159  \tabularnewline
\hline
\end{tabular}
\caption{Informative Features in Different Countries}
\label{table:InfoFeatures}
\end{table*}

>>>>

\begin{table*}
\footnotesize
\begin{tabular}[]{lrrrrrrr}
  \hline
Dataset & a & last a & last o & last consonant & last vocal & 1st consonant & 1st vocal  \tabularnewline
  \hline
  %\endhead
 Uruguay (F) \footnote{F is for females and M is for males} &    0.816 &         0.456 &         0.007 &                 0.287 &             0.712 &                  0.823 &              0.177  \tabularnewline
 Uruguay (M) \footnotemark[3] &    0.643 &         0.249 &         0.062 &                 0.766 &             0.234 &                  0.771 &              0.228  \tabularnewline
 Spain (F) \footnotemark[3]  &    0.922 &         0.588 &          0.03 &                 0.271 &             0.728 &                  0.772 &              0.228  \tabularnewline
 Spain (M) \footnotemark[3]  &    0.818 &          0.03 &         0.268 &                 0.569 &              0.43 &                  0.763 &              0.236  \tabularnewline
 UK (F) \footnotemark[3]     &    0.825 &         0.374 &         0.013 &                 0.322 &             0.674 &                  0.765 &              0.235  \tabularnewline
 UK (M) \footnotemark[3]     &    0.716 &         0.036 &         0.039 &                  0.78 &             0.218 &                  0.799 &                0.2  \tabularnewline
 USA (F) \footnotemark[3]    &    0.816 &         0.456 &         0.007 &                 0.287 &             0.712 &                  0.823 &              0.177  \tabularnewline
 USA (M) \footnotemark[3]    &    0.643 &          0.02 &         0.061 &                 0.765 &             0.234 &                   0.84 &              0.159  \tabularnewline
 Canada (F) \footnotemark[3] &    0.659 &         0.189 &         0.005 &                 0.591 &             0.408 &                  0.838 &              0.16  \tabularnewline
 Canada (M) \footnotemark[3] &    0.752 &          0.22 &         0.025 &                  0.54 &             0.456 &                  0.818 &              0.181  \tabularnewline

\hline
\end{tabular}
\caption{Informative Features in Different Countries}
\label{table:InfoFeatures}
\end{table*}
